---
title: "WINE QUALITY PREDICTION"
author: "Auma"
date: "`r Sys.Date()`"
output: html_document
---
#Wine quality prediction
## Loading packages
```{r }

library(tidyverse)    # metapackage of all tidyverse packages
library(glmnet)
library(e1071)    # for skewness  
library(caret)    # termed as Classification and Regression Training
library(reshape2)
library(data.table) # provides a high-performance version of R’s data.frame
library(caTools)    # sample.split
library(xgboost)    # for building XGBoost model
library(cowplot)    # for combining multiple plots 
library(randomForest)
#library(dplyr)      # data manipulation package i.e Select, Filter, Arrange, Mutate, and Summarize 
#library(ggplot2)    # for ploting 


```

## Importing dataset

```{r }
library(readr)
 train <- read_csv("train.csv")
View(train)
 test <- read_csv("test.csv")
 View(test)
 
```

##plotting missing data

```{r }
library(DataExplorer)
plot_missing(train)
plot_missing(test)


```


```{r }
str(train)
str(test)
```



##Robust Scalar

```{r}
robustscalar<- function(x){
    ( x - median(x) ) / (quantile(x, probs = .75) - quantile(x, probs = .25) )
}
robustscalar_train <- as.data.frame(lapply(train, robustscalar))
head(robustscalar_train)

```

##Z-Score Normalization "Standardization"

```{r}
standardise_train <-  as.data.frame(scale(train[, -c(12)], center = TRUE, scale = TRUE))
standardise_train <- as.data.frame(c(standardise_train, train[, c(12)]))
head(standardise_train)


```

##Retrun all data except column number 12 "quality"

```{r}
x = train[,-c(12)]
y = train[, c(12)]

```

##Correlation Matrix

```{r}
cor_mat = round(cor(train),2)
cor_mat

```

```{r}
shape_cormat <- melt(cor_mat) # reshape2
head(shape_cormat, 7)

```

##plot heat map

```{r}
ggplot(shape_cormat, aes(Var1,Var2, fill=value))+
  scale_fill_gradient2(low = "#FFA07A",
                       mid = "#32CD32",
                       high = "#800000")+
  geom_tile(color='black')+
  geom_text(aes(label=paste(round(value,2))),size=2, color='black')+
  theme(axis.text.x = element_text(vjust=0.5, angle = 65))+
  labs(title='Correlation between each variables',
       subtitle = 'Quality is positive related to alcohol, sulphates, citric acid, fixed acidity; Quality is negative related to volatile acidity',
       x='',y='')

```

```{r}
table(train$quality)

```


```{r}
ggplot(train, aes(quality))+geom_bar(color="#2E8B57",
    fill="#8B008B",)+labs(title='Most are 5 and 6 quality')+theme_bw()

```

### bar plot

```{r}
par(mfrow = c(1, 2), mar = c(5, 4, 2, 1))
 with(subset(train, quality == '5'), plot(alcohol, pH, main = "quality == 5", col = '#FF0000'))
 with(subset(train, quality == '6'), plot(alcohol, pH, main = "quality == 6", col = '#FF0000'))

```

###Multiple histograms 

```{r}
par(mfrow = c(2, 1), mar = c(4, 4, 2, 1))
hist(subset(train, quality == '5')$alcohol, col = '#556B2F', xlab = 'Price', ylab = 'Count', main = 'Histogram of quality(5) Vs quality distribution')
hist(subset(train, quality == '6')$alcohol, col = '#2F4F4F', xlab = 'Price', ylab = 'Count', main = 'Histogram of quality(6) Vs quality distribution')

```

#Create histogram

```{r}

hist(train$quality, breaks = 10, col = '#A0522D', xlab = 'quality', main  = 'Histogram of quality')
```

###scatter plot

```{r}
ggplot(
    data=train, 
    aes(
        x = density,
        y = pH,
        col = quality
    )
) + geom_point()

```

#Quartiles

##describes the value that a given percent of the values are lower than.

##The value of the first quartile cuts off the first 25% of the data
##The value of the second quartile cuts off the first 50% of the data
##The value of the third quartile cuts off the first 75% of the data
##The value of the fourth quartile cuts off the 100% of the data


```{r}

min(train$quality)
quantile(train$quality) 
max(train$quality)

```

```{r}
summary(train)

```

# Divide into test and train date
#train = as.data.frame(train)

```{r}
train$quality = as.factor(train$quality)

set.seed(160)

train_data = sample(1:nrow(train), size = 0.8*nrow(train))
train_set = train[train_data,]
test_set = train[-train_data,]
nrow(train_set)
nrow(test_set)

```

#Dession Trees

```{r}
library(rpart) #for trees
model = naiveBayes(
    quality~., 
    data = train_set,
    method="class"
)
pred = predict(model, newdata=test_set)
confusion_matrix = confusionMatrix(test_set$quality, pred)
confusion_matrix

```

#Naive Bayes

```{r}
model = naiveBayes(
    quality~., 
    data = train_set
)
pred = predict(model, newdata=test_set)
confusion_matrix = confusionMatrix(test_set$quality, pred)
confusion_matrix

```

#Grid Search

```{r}
Control = trainControl(
    method = 'cv', 
    number = 10,
    search = 'grid'
)

```

#Support Vector Machine

```{r}
library(kernlab)

Grid = expand.grid(
    Gamma = 10^seq(-2,2,0.01), 
    Cost = 10^seq(-2,2,0.01)
)

svm_model = train(
    quality~., 
    data = train_set,
    method = 'svmRadial',
    tune.Grid = Grid,
    trControl = Control 
)

```



```{r}
pred = predict(svm_model, newdata=test_set)
confusionMatrix(test_set$quality, pred)

```

# Multinom

```{r}
Grid = expand.grid(
    decay = seq(0,1, 0.02)
)

modelCVlogit = train(
    quality~., 
    data = train_set,
    method = 'multinom', 
    trControl = Control,
    tuneGrid = Grid
)

```

```{r}
pred = predict(modelCVlogit, newdata=test_set)
confusionMatrix(test_set$quality, pred)

```
